Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Updates from Overleaf
Overleaf 2022 01 20 2159 (#13)
* Updates from Overleaf

* Shorted conclusion

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance, the model pre-trained and fine-tuned on NER-pero still gives the best results.
This is probably due to the fact that the texts produced by Pero-OCR feature characteristics intermediary between human transcriptions and Tesseract.
This OCR tool removes the characters recognised with a low confidence, which is probably a great help to the NER.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}F1 scores of NER predictions in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}

>>>>

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance, the model pre-trained and fine-tuned on NER-pero still gives the best results.
This is probably due to the fact that the texts produced by Pero-OCR feature characteristics intermediary between human transcriptions and Tesseract.
This OCR tool removes the characters recognised with low confidence, which is probably a great help to the NER.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}F1-scores of NER predictions in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}
